Medical Concept Extraction

### 2012-12-16 paper/paper.tex
Finished the rest of the results section except for the actual, you know, results.

>>>>

Recall that each model contains three different classifiers: libsvm, liblinear, and crfsuite. So, in total we attempted training 69 classifiers. Unfortunately, as discussed later in the paper, the libsvm classifiers took very long to train and most were not finished in time. Consequently, their results are not included in this report. Fortunately we were able to train a single libsvm classifier from a model that had all of the features enabled.  So, all in all the results include the output from 47 classifiers (46 liblinear and crfsuite classifiers and 1 libsvm classifier).
